A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-29 0_main.tex
new title
restructure results and discussion

%\title{A robust framework for variable extrusion width concentric toolpath generation}
\title{An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
By densely filling consecutive 2D layers with contour-following extrusion toolpaths, FDM can produce parts with high stiffness,
which is especially important for thin parts such as blow molding prototypes and microstructures.
%
Existing approaches using uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape.
Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center.
Our framework makes it possible to distribute the workload of the alterations over larger regions farther from the center.
Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
By carefully formulating various beading schemes for our framework we can emulate existing approaches and we propose a novel approach which incluences a larger region of toolpaths so that the toolpaths are altered less severely.
%
This approach reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
\end{abstract}

@@

\input{10_applications}

>>>>

\title{A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
%
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as blow molding prototypes \jun{this seems not discussed in the main text} and microstructures. 
Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center \jun{only widths in the center?}.
%Our framework makes it possible to distribute the workload of \jun{is the sentence complete if we delete worklaod of} the alterations over larger regions farther from the center. 
In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
%Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
We present various schemes to decide the number of beads and their widths from the center outward.
%By carefully formulating various beading schemes for our framework we can emulate existing approaches.
Furthermore, we propose a novel scheme which influences a larger region of toolpaths so that the toolpaths are altered less severely. \jun{I miss a better summary of this inner distribution scheme.}
%
This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
\end{abstract}

@@
